---
title: "WEEK4"
author: "Lindsay Cooper"
date: "2025-09-09"
output: html_document
---


```{r}
library(helminthR)
dat <- helminthR::loadData()

```
How many rows of data are there for iraq?

Conditional is == 
  - gives true or false equal to the same length as DAT for each row that country = iraq
Which 
  - gives indices corresponding with Iraq = country
Indices nrow
```{r}
x <- nrow(dat[which(dat$country == 'Iraq'),])

y <- subset(dat, dat$country == 'Iraq')
```


```{r echo=TRUE}
tellMeIGood <- function(name){
  nameOfPerson <- name
  print(paste(name, ', you are good'))
}
```

subset - in base, give two arguments, data you want to subset, how you want to subset 

() only for a function, nrow, subset, which, start of if, start of for loop
[] indexing, pulling something out of prexisting object ncommas is how many dimensions of array
{} for loops, if statements, define boundary conditions, if condition is true then {do this}
  - define protocols
  
```{r}

```
mexico used as default

Linking conditionals
what will is.na return -> vector, logical
- can also be an or instead of an and
using | (or)

```{r}
x <- 1:10
if(any(is.na(x) & any(x>2))){
  
}



```


